Formal Analysis of Rate-Monotonic Scheduling Implementation via Real-Time Maude

### 2015-09-09 RMS/submission.tex
finish Sect. RTMaude

A class declaration $\texttt{class }C\texttt{ |
}att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
declares a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
to $s_n$. An \emph{object} of class $C$ in a given state is
represented as a term $\texttt{< } O\texttt{:} C \texttt{ | }
att_1\texttt{:}val_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}val_n\texttt{
  >}$ of sort \verb|Object|, where $O$, of sort \verb|Oid|, is the object's
\emph{identifier}, and where $val_1$ to $val_n$ are the current values of the
attributes $att_1$ to $att_n$. A \emph{subclass} inherits all the attributes
and rules of its superclasses.

\subsection{Formal Analysis}
In this

>>>>

A class declaration $\texttt{class }C\texttt{ |
}att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
declares a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
to $s_n$. An \emph{object} of class $C$ in a given state is
represented as a term $\texttt{< } O\texttt{:} C \texttt{ | }
att_1\texttt{:}val_1\texttt{,} \ldots
\texttt{,}att_n\texttt{:}val_n\texttt{ >}$ of sort \verb|Object|,
where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
where $val_1$ to $val_n$ are the current values of the attributes
$att_1$ to $att_n$. A \emph{subclass} inherits all the attributes and
rules of its superclasses.

\subsection{Formal Analysis}
In this paper, we only consider Real-Time Maude's \emph{linear
  temporal logic model checker}, which analyzes whether \emph{each}
behavior satisfies a temporal logic formula. \emph{State propositions}
are terms of sort \verb|Prop|, and their symantics is defined by
equations $\texttt{ceq } statePattern \texttt{ |= } prop \texttt{ = }
b \texttt{ if } cond$, with $b$ a term of sort \verb|Bool|, stating
that $prop$ evaluates to $b$ in states that are instances of
$statePattern$ when the condition $cond$ holds. These equations
together define $prop$ to hold in all states $t$ where $t \texttt{ |=
} prop$ evaluates to \verb|true|. A temporal logic \emph{formula} is
constructed by state propositions and temporal logic operators such as
\verb|True|, \verb|False|, \verb|~|(negation), \verb|/\|, \verb|\/|,
\verb|->|(implication), \verb|[]|(``always''),
\verb|<>|(``eventually'') and \verb|U|(``until''). Real-Time Maude
provides both \emph{unbounded} and \emph{time-bounded} LTL model
checking. The time-bounded model checking command
\begin{alltt}
  (mc \(t\) |=t \(formula\) in time <= \(timeLimit\) .)
\end{alltt}
checks whether the temporal logic formula holds in all behaviors up to
duration $timeLimit$ starting from the initial state $t$.
